Clustering based on probability distributions with application on residential customers

### 2021-10-19 main.Rmd
adding validation section

tab_dist <- tibble::tibble(granularity = granularity, `alternate distribution` = alternate_design)

@@

```{r tab-design}
design = c("design-1", "design-2", "design-3", "design-4", "design5")
g1 = c("null", "alternate", "null", "null", "alternate")
g2 = c("null", "null", "alternate", "null", "alternate")
g3 = c("null", "null", "null", "alternate", "alternate")
table <- tibble(design, g1, g2, g3)

# %>% kable(caption = "5 different designs resulting from considering different distributions across categories.")
```

@@

```{r plot-3gran-new, out.width="100%", fig.cap="The linear (left) and cyclic (right) representation of the measured variable is shown. In this scenario, all of $g1$, $g2$ and $g3$ changes across at least one design. Also, it is not possible to comprehend these patterns across cyclic granularities or group similar series just by looking at the linear plots."}

@@

p4 <- ggplot(data_bind, aes(x = as.factor(g3), y = sim_data)) + geom_boxplot(alpha =0.5) +
  xlab("g3") + theme_bw()+
  facet_wrap(~design, scales = "free_y", ncol = 1)+ stat_summary(
    fun = median,
    geom = 'line',
    aes(group = 1), size = 0.8, colosr = "blue")+ ylab("")+
  theme_validation()

@@

p4 <- ggplot(data_bind, aes(x = as.factor(g3), y = sim_data)) + geom_boxplot(alpha =0.5) +
  xlab("g3") + theme_bw()+
  facet_wrap(~design, scales = "free_y", ncol = 1)+ stat_summary(
    fun = median,
    geom = 'line',
    aes(group = 1), size = 0.8, colosr = "blue")+ ylab("")+
  theme_validation()

(p1 + (p2 + p3 + p4)) *
  theme_validation() + plot_layout(widths = c(2, 1))

@@

@@

@@

((p1 + p_null)/( p2 + p_varf)/(p3 + p_varx)/(p4 + p_varall))

@@

```{r}
# code in append_3gran_change.R
table <- read_rds("data/append_3gran_change.rds")
table %>% kable()
```

@@

wkndwday <- read_rds(here("data/dist_gran_wkndwday_356cust_robust.rds")) %>% broom::tidy()

moy <- read_rds(here("data/dist_gran_moy_356cust.rds")) %>% broom::tidy()

hod <- read_rds(here("data/dist_gran_hod_356cust_robust.rds")) %>% broom::tidy()

>>>>

tab_dist <- tibble::tibble(granularity = granularity, `Varying distributions` = alternate_design)

@@

```{r tab-design}
design = c("design-1", "design-2", "design-3", "design-4", "design-5")
g1 = c("fixed", "vary", "fixed", "fixed", "vary")
g2 = c("fixed", "fixed", "vary", "fixed", "vary")
g3 = c("fixed", "fixed", "fixed", "vary", "vary")
table <- tibble(design, g1, g2, g3)

#%>% kable(caption = "5 different designs resulting from considering different distributions across categories.")
```

@@

```{r plot-3gran-new, out.width="100%", fig.cap="The linear (left) and cyclic (right) representation of the measured variable is shown. In this scenario, all of $g1$, $g2$ and $g3$ changes across at least one design. Also, it is not possible to comprehend these patterns across cyclic granularities or group similar series just by looking at the linear plots.", fig.pos="htb"}

@@

@@

gran2_change <- (p2 + p3 + p4) *
  theme_validation()
```

@@

gran1_change <- (p2 + p3 + p4) *
  theme_validation()
# 
# plot_cyclic_data( data_bind %>% filter(design=="design2"))
# plot_data( data_bind %>% filter(design=="design3"))
# plot_data( data_bind %>% filter(design=="design4"))
# plot_data( data_bind %>% filter(design=="design5"))
```

@@

```{r gran2and1-clubbed, fig.cap=" For the left scenario $g1$, $g2$ would change across atleast one design but $g3$ change remains same across all design. For tthe right one, only $g3$ changes across different designs."}
#gran2_change  + gran1_change + plot_layout(widths = c(1,1))
ggpubr::ggarrange(gran1_change, gran2_change, labels = c("a", "b"))
```

@@

#((p1 + p_null)/( p2 + p_varf)/(p3 + p_varx)/(p4 + p_varall)) 
#p_null+ p_varf + p_varx + p_varall
ggpubr::ggarrange(p_null, p_varf, p_varx, p_varall, labels = c("Design-1", "Design-2", "Design-3", "Design-4"))

@@

```{r, eval=FALSE}
# code in append_3gran_change.R
table <- read_rds("data/append_3gran_change.rds")
table %>% kable()
```

@@

wkndwday <- read_rds(here("data/dist_gran_wkndwday_356cust_robust.rds")) 
#%>% broom::tidy()

moy <- read_rds(here("data/dist_gran_moy_356cust.rds")) 
#%>% broom::tidy()

hod <- read_rds(here("data/dist_gran_hod_356cust_robust.rds")) 
#%>% broom::tidy()
